Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Byzantium revision (\YellowPaperVersionNumber{})}}

### 2018-01-25 Paper.tex
Change hypertarget captions to empty strings

I define a number of useful functions throughout. \hypertarget{ell}{ell}One of the more common is $\ell$, which evaluates to the last item in the given sequence:

@@

The account state comprises the following four fields:\hypertarget{account_nonce}{account nonce}

>>>>

I define a number of useful functions throughout. \hypertarget{ell}{}One of the more common is $\ell$, which evaluates to the last item in the given sequence:

@@

The account state comprises the following four fields:\hypertarget{account_nonce}{}
